eu-circle_case-study-2

### 2017-05-05 EU-Circle/eu-circle_case-study-1.Rmd
EU-Circle R-markdowns

```{r, warning=FALSE}
if (!file.exists('dse.mld.t2m.rda')) {
  dse.mld.t2m <- DSensemble.eof(eof.res,predictor=T2M,it='mjjas',path="~/data/CMIP5.monthly",pattern = "tas_Amon_ens_")
  save(dse.mld.t2m,file = 'dse.mld.t2m.rda')
} else load('dse.mld.t2m.rda')
plot(dse.mld.t2m)
```

@@

```{r}
dse.mld <- dse.mld.slp
gcmnm <- names(dse.mld)
gcmnm <- gcmnm[-grep('info',gcmnm)]; gcmnm <- gcmnm[-grep('eof',gcmnm)]
for (nm in gcmnm) {
  coredata(dse.mld[[nm]]) <- coredata(dse.mld.slp[[nm]]) + coredata(dse.mld.t2m[[nm]])
}
```

>>>>

```{r, warning=FALSE, eval=FALSE,echo=FALSE}
if (!file.exists('dse.mld.t2m.rda')) {
  dse.mld.t2m <- DSensemble.eof(eof.res,predictor=T2M,it='mjjas',path="~/data/CMIP5.monthly",pattern = "tas_Amon_ens_")
  save(dse.mld.t2m,file = 'dse.mld.t2m.rda')
} else load('dse.mld.t2m.rda')
plot(dse.mld.t2m)
```

@@

```{r, eval=FALSE,echo=FALSE}
dse.mld <- dse.mld.slp
gcmnm <- names(dse.mld)
gcmnm <- gcmnm[-grep('info',gcmnm)]; gcmnm <- gcmnm[-grep('eof',gcmnm)]
for (nm in gcmnm) {
  coredata(dse.mld[[nm]]) <- coredata(dse.mld.slp[[nm]]) + coredata(dse.mld.t2m[[nm]])
}
```

### 2017-05-05 EU-Circle/eu-circle_case-study-2.Rmd
EU-Circle R-markdowns

```{r}
load('cyclones.baltic.rda')
map(cyclones.baltic)
```

@@

```{r}
plot(cyclones.baltic)
```

@@

```{r,warning=FALSE}
if (!file.exists('eu-circle_case-study-2_slp.rda')) {
  x <- retrieve('pp_0.25deg_reg.nc',path='~/storeB/data/data.ECAD',
                lon=c(10,30),lat=c(53,66))
  save(file='eu-circle_case-study-2_slp.rda',x)
} else load('eu-circle_case-study-2_slp.rda')
## Only keep the ECAD data
map(x,FUN='q95',new=TRUE)
diagnose(x)
```

@@

Calculate the geostrophic wind based on the slp data.

@@

```{r}
baltic.events <- c(19931010,20000328,20010328,20040313,20060330,20081017,20081202,20091002,20100128)
uv <- geostrophicwind(x)
```

>>>>

```{r}
load('cyclones.baltic.rda')
map(cyclones.baltic,new=FALSE)
```

@@

```{r}
plot(cyclones.baltic,new=FALSE)
```

@@

```{r,warning=FALSE}
if (!file.exists('eu-circle_case-study-2_slp.rda')) {
  x <- retrieve('pp_0.25deg_reg.nc',path='~/storeB/data/data.ECAD',
                lon=c(10,30),lat=c(53,66))
  save(file='eu-circle_case-study-2_slp.rda',x)
} else load('eu-circle_case-study-2_slp.rda')
## Only keep the ECAD data
map(x,FUN='q95',new=FALSE)
```

@@

Calculate the geostrophic wind based on the slp data from EOBS.

@@

NOT FINISHED

```{r, eval=FALSE,echo=FALSE}
baltic.events <- c(19931010,20000328,20010328,20040313,20060330,20081017,20081202,20091002,20100128)
if (!file.exists('uv.rda')) {
  uv <- geostrophicwind(x)
  save(uv,file='uv.rda')
} else load('uv.rda')
```
